Preparing articles for submission to the \\ Archive of Numerical Software

### 2011-06-03 paper.tex
More work on style file and instructions.
git-svn-id: https://svn.mathsim.eu/documents/publications/journal/style@2730 a653633e-0a08-0410-9ecb-ed4064e9718a

% $Id$
\documentclass{ansarticle}

@@

@@

\begin{abstract}
  This document describes the general structure of the
  \texttt{ansarticle} document class and serves as an example for its
  usage. \texttt{ansarticle.cls} is based on the standard \LaTeX{}
  \texttt{article.cls} and a few other standard packages. It fixes
  style parameters to the preferred style of the Archive of Numerical
  Software (ANS).
\end{abstract}

@@

To write an article for ANS, you need to download the following files
from the ANS web page:
\begin{itemize}
\item
  \emp{paper.tex}, the source file for this document and a template for
  authors;
\item
  \emp{ansarticle.cls}, the ANS document class file;
\item
  \emp{anslistings.sty}, the ANS style file for typesetting of code;
\item
  \emp{bibliography.bib}, a bibliography with some important
  references;
\item
  \emp{Makefile}, useful for building your document.
\end{itemize}

The file \texttt{ansarticle.cls} loads the standard LaTeX
\texttt{article.cls} and some additional packages. It also sets up the
layout. Hardly any of the options of the packages are available to the
author, in order to keep the journal style consistent.

Upon loading, \texttt{ansarticle.cls} requires the following packages:
\emp{a4wide},
\emp{anslistings},
\emp{algorithm},
\emp{algorithmicx},
\emp{amsmath},
\emp{amssymb},
\emp{booktabs},
\emp{fancyhdr},
\emp{graphicx},
\emp{hyperref},
\emp{authblk},
\emp{lastpage},
\emp{listings.}
These packages are part of standard \TeX{} distributions and should
not cause any difficulties.

@@

The ANS document class uses the amsmath and amssymb packages for
improved typesetting of mathematical formul\ae like, e.g., this one:
\begin{equation}
  \cfrac{1}{\sqrt{2}+
    \cfrac{1}{\sqrt{2}+
      \cfrac{1}{\sqrt{2}+\dotsb
  }}}.
\end{equation}

Make sure that you familiarize yourself with the \emp{amsmath}
environments \emp{multline}, \emp{align} and \emp{split} (and know the
differences between them). Avoid home-made splitting using
\emp{\{array\}\{rcl\}}.

@@

\fixme{Write something about typesetting tables with \emp{booktabs}.}

@@

All code listings are based on the \texttt{listings}
package~\cite{HeinzMoses07}. The style file \texttt{anslistings.sty},
automatically included by \texttt{ansarticle.cls}, provides standard
styles for a variety of common programming languages. Changing any
listing style parameters is not encouraged and may lead to unexpected
outcomes in the final publication.

Below, we provide samples of listings for the languages available. If
a language is missing, please contact the managing editor for an
updated style file.

@@

\fixme{Adjust width of code box, a little too wide now.}

@@

Alternatively, it is possible to use
\lstinline[language=TeX]!\inputcpp{file.cc}!  to print the C++ code in
a file. Here is an example what C++ code looks like.

@@

\subsubsection{Python}
can be typeset as well.

\begin{python}
# Time-stepping
t = dt
p = Progress("Time-stepping")
while t < T + DOLFIN_EPS:

    # Update pressure boundary condition
    p_in.t = t

    # Compute tentative velocity step
    begin("Computing tentative velocity")
    b1 = assemble(L1)
    [bc.apply(A1, b1) for bc in bcu]
    solve(A1, u1.vector(), b1, "gmres", "ilu")
    end()

    # Pressure correction
    begin("Computing pressure correction")
    b2 = assemble(L2)
    [bc.apply(A2, b2) for bc in bcp]
    solve(A2, p1.vector(), b2, "gmres", "amg_hypre")
    end()

    # Velocity correction
    begin("Computing velocity correction")
    b3 = assemble(L3)
    [bc.apply(A3, b3) for bc in bcu]
    solve(A3, u1.vector(), b3, "gmres", "ilu")
    end()

@@

    # Move to next time step
    u0.assign(u1)
    p.update(t / T)
    t += dt
\end{python}

@@

Additional material, chich is not part of the article text, but part
of the submission, for instance setup scripts or video output, can be
linked from the article, using the \texttt{hyperref} commands
(\texttt{hyperref} is automaticly included by
\texttt{ansarticle}). URLs to such material should start with the
filename. A suitable prefix will be added to the links in the
editorial process.

@@

Create a file \texttt{ansinfo.tex} in the same directory. The file
contains macros defining the publication information like in the
following listing:

@@

@@

Excerpt from~\cite{Newton1687}.

@@

\subparagraph{A subparagraph} If you really want to nest that deeply, go
ahead! But, while you might have enjoyed
reading~\cite{Wittgenstein21,Wittgenstein81}, you are encouraged to
question the applicability to a publication on a thing as profane as
software.

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

>>>>

% $Id$

\documentclass{ansarticle}

@@

\fixme{Who should be listed as authors on this document?}

@@

\begin{abstract}
  This document describes the general structure of the
  \emp{ansarticle} document class and serves as an example for its
  usage. The \emp{ansarticle} document class is based on the standard
  \LaTeX{} \emp{article} document class and a few other standard
  packages. It fixes style parameters to the preferred style of the
  Archive of Numerical Software (ANS).
\end{abstract}

@@

To write an article for ANS, you need to download the following files
from the ANS web page:
\begin{itemize}
\item
  \emp{paper.tex}, the source file for this document and a template for
  authors;
\item
  \emp{ansarticle.cls}, the ANS document class file;
\item
  \emp{anslistings.sty}, the ANS style file for typesetting of code;
\item
  \emp{bibliography.bib}, a bibliography with some important
  references;
\item
  \emp{Makefile}, useful for building your document.
\end{itemize}
These files are all included in the tarball \emp{ansarticle.tar.gz}.

The file \emp{ansarticle.cls} loads the standard LaTeX
\emp{article.cls} and some additional packages. It also sets up the
layout. Hardly any of the options of the packages are available to the
author, in order to keep the journal style consistent.

Upon loading, \emp{ansarticle.cls} requires the following packages:
\emp{a4wide},
%\emp{anslistings},
\emp{algorithm}, \emp{algorithmicx}, \emp{algpseudocode},
\emp{authblk},
\emp{amsmath}, \emp{amssymb},
\emp{booktabs},
\emp{fancyhdr},
\emp{graphicx},
\emp{hyperref},
\emp{lastpage},
\emp{listings},
\emp{todonotes}.
These packages are part of standard \LaTeX{} distributions and should
not cause any difficulties.

@@

The ANS document class uses the \emp{amsmath} and \emp{amssymb}
packages for improved typesetting of mathematical formul\ae like,
e.g., this one:
\begin{equation}
  \cfrac{1}{\sqrt{2}+
    \cfrac{1}{\sqrt{2}+
      \cfrac{1}{\sqrt{2}+\dotsb
  }}}.
\end{equation}

Make sure that you familiarize yourself with the \emp{amsmath}
environments \emp{multline}, \emp{align} and \emp{split} (and know the
differences between them). Avoid home-made splitting using
\emp{\{array\}\{rcl\}}. For details, refer to the \emp{amsmath}
documentation.

@@

Use the commands provided by the \emp{booktabs} package for better
looking typesetting of tables, as illustrated in
Table~\ref{tab:tableexample}.

\begin{table}
  \begin{center}
    \begin{tabular}{lcc}
      \toprule
      Entity & Dimension & Codimension \\
      \hline
      Vertex & $0$ & $D$ \\
      Edge & $1$ & $D-1$ \\
      Face & $2$ & $D-2$ \\
      & & \\
      Facet & $D-1$ & $1$ \\
      Cell & $D$ & $0$ \\
      \bottomrule
    \end{tabular}
  \end{center}
    \caption{Mesh entities and their dimensions/codimensions.}
    \label{tab:tableexample}
\end{table}

\subsection{Typesetting algorithms}

Use the functionality provided by the packages \emp{algorithm},
\emp{algorithmic} and \emp{algpseudocode}, automatically included by
the \emp{ansarticle} document class, to typeset algorithms. This is
illustrated in Algorithm~\ref{alg:algorithmexample}.

\begin{algorithm}
  \begin{algorithmic}
    \State $D^{0,0}(x,y) := 1$
    \State $D^{1,0}(x,y) := \frac{1+2x+y}{2}$
    \For{$p \gets 1$, $d-1$}
    \State $D^{p+1,0}(x,y) := \left( \frac{2p+1}{p+1} \right)
    \left( \frac{1 + 2x + y}{2} \right) D^{p,0}(x,y)
    - \left( \frac{p}{p+1} \right) \left( \frac{1-y}{2} \right)^2
    D^{p-1,0}(x,y)$
    \EndFor
    \For{$p \gets 0,d-1$}
    \State $D^{p,1}(x,y) := D^{p,0}(x,y) \left( \frac{1+2p+(3+2p) y}{2} \right)$
    \EndFor
    \For{$p \gets 0,d-1$}
    \For{$q \gets 1,d-p-1$}
    \State $D^{p,q+1}(x,y) :=
    \left( a_{q}^{2p+1,0} y + b_q^{2p+1,0} \right) D^{p,q}(x,y)
    - c_q^{2p+1,0} D^{p,q-1}(x,y)$
    \EndFor
    \EndFor
  \end{algorithmic}
  \caption{Compute all triangular orthogonal polynomials up to degree
    $d$ by recurrence}
  \label{dubalg}
\end{algorithm}

@@

All code listings are based on the \emp{listings}
package~\citep{HeinzMoses07}. The package \emp{anslistings},
automatically included by \emp{ansarticle} document class, provides
standard styles for a variety of common programming
languages. Changing any style parameters for this package is not
encouraged and may lead to unexpected outcomes in the final
publication.

Below, we provide samples of listings for the some of the languages
available. If a language is missing, please contact the managing
editor for an updated style file.

@@

@@

Alternatively, it is possible to use
\lstinline[language=TeX]!\inputcpp{file.cc}!  to print the C++ code in
a file. Here is an example of typesetting of C++ code:

@@

\subsubsection{Python}

The following illustrates typesetting of Python code:

\begin{python}
# Time-stepping
t = dt
while t < T:

    # Compute tentative velocity step
    b1 = assemble(L1)
    [bc.apply(A1, b1) for bc in bcu]
    solve(A1, u1.vector(), b1, "gmres", "ilu")

    # Pressure correction
    b2 = assemble(L2)
    [bc.apply(A2, b2) for bc in bcp]
    solve(A2, p1.vector(), b2, "gmres", "amg_hypre")

    # Velocity correction
    b3 = assemble(L3)
    [bc.apply(A3, b3) for bc in bcu]
    solve(A3, u1.vector(), b3, "gmres", "ilu")

@@

    # Move to next time step
    u0.assign(u1)
    t += dt
\end{python}

@@

Additional material which is not part of the article text, but part of
the submission, for instance setup scripts or video output, can be
linked from the article, using the \emp{hyperref} commands
(\emp{hyperref} is automaticly included by
\emp{ansarticle}). URLs to such material should start with the
filename. A suitable prefix will be added to the links in the
editorial process.

\subsection{Citations}

The \emp{ansarticle} document class imports the \emp{natbib} package,
which provides the commands \emp{\textbackslash{}citet\{\}} and
\emp{\textbackslash{}citep\{\}}. These should be used in place of the
regular \emp{\textbackslash{}cite\{\}} command as illustrated by the
following passage: It was found by \citet{Wittgenstein1921} that what
we cannot speak about we must pass over in silence, contrary to common
belief~\citep{Newton1687}.

\subsection{Other}

The \emp{ansarticle} document class provides a number of useful
notation macros which you can find by browsing through the file
\emp{ansarticle.cls}.

\subsection{Checklist}

\fixme{Add more things to this checklist!}

Before submitting your manuscript to ANS, please review the following
checklist:
\begin{itemize}
\item
  Have you run a spell checker on your manuscript (using an American English
  dictionary)?
\item
  Have you referred to all figures and tables (callouts)?
\item
  Have you used a scalable vector graphics format for all images where
  possible?
\end{itemize}

@@

Create a file \emp{ansinfo.tex} in the same directory. The file
contains macros defining the publication information like in the
following listing:

@@

\fixme{Should this section contain some more info?}

@@

\fixme{Add missing references (Newton and Wittgenstein) to
  bibliography.}

\fixme{Also add main references for all libraries listed on the ANS
  web page.}

\fixme{Can we cut down some on the text here? It's pretty long.}

Excerpt from~\citet{Newton1687}.

@@

\subparagraph{A subparagraph} If you really want to nest that deeply, go
ahead! But, while you might have enjoyed
reading~\citet{Wittgenstein1921,Wittgenstein1981}, you are encouraged to
question the applicability to a publication on a thing as profane as
software.

@@
